---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

```{r, echo=F}
load('tests/testthat/test_df.RData')
```


# mdftracks

Reads and writes **[MTrackJ](https://imagescience.org/meijering/software/mtrackj/) Data Files** ([`.mdf`](https://imagescience.org/meijering/software/mtrackj/format/)).
Supports clusters, 2D data, and channel information. If desired, generates
unique track identifiers based on cluster and id data from the `.mdf` file.

## Usage

**Reading 3D data: **

```{r, eval=F}
library(mdftracks)
data <- read.mdf('~/mdftracks.mdf')
head(data, 10)
```

```{r, echo=F}
library(mdftracks)
data <- read.mdf('~/stack/mtrackj/121120_RCM_HBC_cell density_complete_p04.mdf')
head(data, 10)
```

**Reading 2D data: **

```{r, eval=F}
library(mdftracks)
data <- read.mdf('~/mdftracks.mdf', drop.Z = T)
head(data, 10)
```

```{r, echo=F}
library(mdftracks)
data <- read.mdf('~/stack/mtrackj/121120_RCM_HBC_cell density_complete_p04.mdf', drop.Z = T)
head(data, 10)
```

**Writing data in `(id, t, x, y, z)` format (eg. from [MotilityLab](https://github.com/jtextor/MotilityLab)):  **

```{r, echo=FALSE}
tracks <- test.df[,c('uid', 't', letters[24:26])]
```

```{r, collapse=FALSE}
print(tracks)
write.mdf(tracks)
```

**Writing data with cluster, channel, and point information: **

```{r, echo=FALSE}
tracks <- test.df
```

```{r, collapse=FALSE}
print(tracks)
write.mdf(tracks, cluster.column = 'cl', id.column = 'id', 
          pos.columns = letters[24:26], channel.column = 'ch', 
          point.column = "p")
```

For more information, consult the function documentation.

## Installation

With the `devtools` package installed:

```{r, eval=F}
install_github('burgerga/mdftracks')
```
